A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-05-12 paper/paper-jsdse/paper-jsdse.tex
nicks comment on year
Incorporate Nick's suggestions.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  ID: the respondents' ID.
\item
  EXPER: temporal scale, i.e., the length of time (years) in the workforce, starting on the respondents' first day at work.
\item
  LNW: natural logarithm of wages, adjusted with 1990's inflation rate.
\item
  BLACK: binary variable, 1 indicates Black and 0 otherwise.
\item
  HISPANIC: binary variable, 1 indicates Hispanic and 0 otherwise.
\item
  HGC: the highest grade completed.
\item
  UERATE: the unemployment rate of the year of the survey. When missing, the variable is set to be 7.875 (the average rate).
\end{enumerate}

@@

Our final target data will include the demographic variables (variable names): sex (\texttt{sex}), race (\texttt{race}), age (\texttt{age\_1979}), highest grade completed reported in each round of the survey (\texttt{grade}), highest grade completed ever reported (\texttt{hgc}), highest grade completed in terms of years, e.g., 9th grade = 9, 3rd-year college = 15, (\texttt{hgc\_i}), highest grade completed in 1979 (\texttt{hgc\_1979}) and whether the graduate equivalency diploma is obtained (\texttt{ged}).

@@

For \texttt{stwork} variable, we only rename the column names from \texttt{new\_data\_qnames}. This variable is then used to calculate the next variable, \texttt{yr\_wforce} for each survey round, which is the year of survey (\texttt{year}) minus the year of individual started working (\texttt{stwork}). Finally, \texttt{exp} variable is derived from the number of weeks worked since the last interview indicated as variable started with \texttt{WKSWK} in \texttt{new\_data\_qnames}. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to year.

@@

Lastly, the individuals in the dropouts subset of the refreshed data (as matched by their \texttt{id}s) belong to the same race as the individuals in the original data. This is also the case in the \texttt{sex} variables, which all correspond to males.

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  ID: the respondents' ID.
\item
  EXPER: stands for experience, the temporal scale, i.e., the length of time (years) in the workforce, starting on the respondents' first day at work.
\item
  LNW: natural logarithm of wages, adjusted with 1990's inflation rate.
\item
  BLACK: binary variable, 1 indicates Black and 0 otherwise.
\item
  HISPANIC: binary variable, 1 indicates Hispanic and 0 otherwise.
\item
  HGC: the highest grade completed.
\item
  UERATE: the unemployment rate of the year of the survey. When missing, the variable is set to be 7.875 (the average rate).
\end{enumerate}

@@

Our final target data will include the demographic variables (variable names): sex (\texttt{sex}), race (\texttt{race}), age (\texttt{age\_1979}), highest grade completed reported in each round of the survey (\texttt{grade}), highest grade completed ever reported (\texttt{hgc}), highest grade completed in terms of years (as an integers), e.g., 9th grade = 9, 3rd-year college = 15, (\texttt{hgc\_i}), highest grade completed in 1979 (\texttt{hgc\_1979}) and whether the graduate equivalency diploma is obtained (\texttt{ged}).

@@

For \texttt{stwork} variable, we only rename the column names from \texttt{new\_data\_qnames}. This variable is then used to calculate the next variable, \texttt{yr\_wforce} for each survey round, which is the year of survey (\texttt{year}) minus the year of individual started working (\texttt{stwork}). Finally, \texttt{exp} variable is derived from the number of weeks worked since the last interview indicated as variable started with \texttt{WKSWK} in \texttt{new\_data\_qnames}. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to fractional year.

@@

Lastly, the matching of individuals in the dropouts subset of the refreshed data with the original data was done using their \texttt{id}s. (Only males were in the original data.) It was comforting to see that all of the individuals in both sets do match on sex (all are male!), and race.

### 2022-05-12 paper/paper.Rmd
nicks comment on year
Incorporate Nick's suggestions.

1. ID: the respondents' ID. 
2. EXPER: temporal scale, i.e., the length of time (years) in the workforce, starting on the respondents' first day at work.
3. LNW: natural logarithm of wages, adjusted with 1990's inflation rate. 
4. BLACK: binary variable, 1 indicates Black and 0 otherwise. 
5. HISPANIC: binary variable, 1 indicates Hispanic and 0 otherwise. 
6. HGC: the highest grade completed.
7. UERATE: the unemployment rate of the year of the survey. When missing, the variable is set to be 7.875 (the average rate).

@@

Our final target data will include the demographic variables (variable names): sex (`sex`), race (`race`), age (`age_1979`), highest grade completed reported in each round of the survey (`grade`), highest grade completed ever reported (`hgc`), highest grade completed in terms of years, e.g., 9th grade = 9, 3rd-year college = 15, (`hgc_i`), highest grade completed in 1979 (`hgc_1979`) and whether the graduate equivalency diploma is obtained (`ged`).

@@

For `stwork` variable,  we only rename the column names from `new_data_qnames`. This variable is then used to calculate the next variable, `yr_wforce` for each survey round, which is the year of survey (`year`) minus the year of individual started working (`stwork`). Finally, `exp` variable is derived from the number of weeks worked since the last interview indicated as variable started with `WKSWK` in `new_data_qnames`. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to year.

>>>>

1. ID: the respondents' ID. 
2. EXPER: stands for experience, the temporal scale, i.e., the length of time (years) in the workforce, starting on the respondents' first day at work.
3. LNW: natural logarithm of wages, adjusted with 1990's inflation rate. 
4. BLACK: binary variable, 1 indicates Black and 0 otherwise. 
5. HISPANIC: binary variable, 1 indicates Hispanic and 0 otherwise. 
6. HGC: the highest grade completed.
7. UERATE: the unemployment rate of the year of the survey. When missing, the variable is set to be 7.875 (the average rate).

@@

Our final target data will include the demographic variables (variable names): sex (`sex`), race (`race`), age (`age_1979`), highest grade completed reported in each round of the survey (`grade`), highest grade completed ever reported (`hgc`), highest grade completed in terms of years (as an integers), e.g., 9th grade = 9, 3rd-year college = 15, (`hgc_i`), highest grade completed in 1979 (`hgc_1979`) and whether the graduate equivalency diploma is obtained (`ged`).

@@

For `stwork` variable,  we only rename the column names from `new_data_qnames`. This variable is then used to calculate the next variable, `yr_wforce` for each survey round, which is the year of survey (`year`) minus the year of individual started working (`stwork`). Finally, `exp` variable is derived from the number of weeks worked since the last interview indicated as variable started with `WKSWK` in `new_data_qnames`. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to fractional year.
